---
title: "Exploring the mtcars Dataset with Shiny"
format: 
  html: 
    toc: true
    shiny: true
---

# Introduction

The `mtcars` dataset in R contains data extracted from the 1974 Motor Trend US magazine. This analysis aims to explore the relationship between a car's fuel efficiency (mpg) and its weight (wt).

# Data Summary

Let's first take a look at the structure and the first few rows of the dataset.

```{r}
# Display the structure
str(mtcars)

# Display the first few rows
head(mtcars)
```

# Data Visualization

We will now create a scatter plot to visualize the relationship between `mpg` and `wt`.

```{r}
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(title = "Scatter Plot of MPG vs Car Weight",
       x = "Weight of the Car",
       y = "Miles per Gallon")
```

# Statistical Summary

Here's a statistical summary of the `mtcars` dataset.

```{r}
summary(mtcars)
```

# Conclusion

From the scatter plot, we observe a negative relationship between the weight of the car and its fuel efficiency. As the weight increases, the miles per gallon tend to decrease.

------------------------------------------------------------------------

# Extra Challenge: Interactive Element with Shiny

```{r}
library(shiny)

# UI for the slider
sliderInput("mpgRange", "Select MPG Range:",
            min = min(mtcars$mpg),
            max = max(mtcars$mpg),
            value = c(min(mtcars$mpg), max(mtcars$mpg)))

# Server logic for plot output
output$mpgPlot <- renderPlot({
    filtered <- mtcars[mtcars$mpg >= input$mpgRange[1] & mtcars$mpg <= input$mpgRange[2], ]
    ggplot(filtered, aes(x = wt, y = mpg)) +
      geom_point() +
      labs(title = paste("Scatter Plot of MPG vs Car Weight for MPG range:", 
                         input$mpgRange[1], "-", input$mpgRange[2]),
           x = "Weight of the Car",
           y = "Miles per Gallon")
})

# Render the plot
plotOutput("mpgPlot")
```
